Estimating Gaze Duration Error from Eye Tracking Data

### 2022-09-23 paper/paper.tex
paper update

Increasingly, eye tracking applications are built using machine learning models trained on 
data sets containing combinations of facial images and fixation coordinates collected 
through careful application design. The resulting gaze fixation prediction model can 
then be applied sequentially to determine how long a subject fixated on a given object.
Thus, gaze duration is derived from aggregation of gaze fixation.

@@

>>>>

Increasingly, eye tracking applications are built using devices that employ 
machine learning models trained to predict fixation locations from a camera image.
While this approach to eye tracking may suffer in terms of accuracy, it can
open up possibilities to researchers that head position restricting devices prevent
\cite{Valtakari2021}.

@@

Discuss error elments around accuracy and precision \cite{Holmqvist2022}
